\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-18 papers/itsc_2012/submitted2.tex
results from worker threads deterministically passed into sim

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
determinism may break down when generators use worker threads, since routes
could be computed in different orders, causing agents to enter the road at
different times.}. After setting up a scenario in the UI, users can save this
configuration for re-simulation.

>>>>

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
determinism may break down when generators use worker threads while the
simulation is running, since tasks may finish and agents may enter the road at
different times}. After setting up a scenario in the UI, users can save this
configuration for re-simulation.
